---
title: "Supplementary_Figure3.rmd"
author: "Michael Noe"
date: "2024-01-26"
output: html_document
---

```{r}
dir.create("../../cfepigenetics_data")
dir.create("../../cfepigenetics_data/diff_startfrags_3bp")
dir.create("../../cfepigenetics_data/diff_startfrags_4bp")
```


## Process the data

*analysis/code/diff_startfrags_3bp.sh* -> outputs "../../cfepigenetics_data/diff_startfrags_3bp"
    Collect information on fragments starting and ending around motifs with a methylated or unmethylated CpG. This script is focused on 3bp-motifs.
*analysis/code/diff_startfrags_4bp.sh* -> outputs "../../cfepigenetics_data/diff_startfrags_4bp"
    Collect information on fragments starting and ending around motifs with a methylated or unmethylated CpG. This script is focused on 4bp-motifs.  


## Pre-requisites

These packages are necessary to make the data-structure that are necessary to make Supplementary Figure 3.

```{r}
```


## Construct files with metrics of fragment starting and ending around motifs

```{r}
ls <- list.files("../../cfepigenetics_data/diff_startfrags_3bp", full.names = T)
m <- matrix(0,16,51)
for (f in ls) {
  print(basename(f))
  temp <- readRDS(f)
  m <- m + temp
}
saveRDS(m, "../data/diff_startfrags_3bp.rds")

ls <- list.files("../../cfepigenetics_data/diff_startfrags_4bp", full.names = T)
m <- matrix(0,16,51)
for (f in ls) {
  print(basename(f))
  temp <- readRDS(f)
  m <- m + temp
}
saveRDS(m, "../data/diff_startfrags_4bp.rds")
```