---
title: "Pre_Supplementary_Figure4.Rmd"
author: "Michael Noe"
date: "`r Sys.Date()`" 
output:
  workflowr::wflow_html:
    toc: false
editor_options:
  chunk_output_type: console
---


## Prerequisites:

These packages are necessary to process the data for Supplementary_Figure4.Rmd
and Supplementary_Figure6.Rmd

```{r packages, echo=FALSE}
library("tidyverse")
library("here")
```


```{r}
outdir <- here("output", "Pre_Supplementary_Figure4.Rmd")
dir.create(outdir)
dir.create(here(outdir, "Loyfer_combined")
```


## Process the data from the Loyfer et al. 

  Download and extract the data (from command line in the newly created directory)
  
  `wget ftp://ftp.ncbi.nlm.nih.gov/geo/series/GSE186nnn/GSE186458/suppl/GSE186458_RAW.tar`
  `tar -xvf GSE186458_RAW.tar`
  
  Install wgbs_tools
  
  `git clone https://github.com/nloyfer/wgbs_tools.git`
  `cd wgbs_tools`
  `python setup.py`
  `wgbstools init_genome hg19`


## Process the files

```{r}
t <- read.table(here(outdir, "wgbs_tools/references/hg19/CpG.bed.gz"))
loc <- "GSE186458_RAW"
ls <- list.files(loc)
ls <- ls[-grep("hg38", ls)]

lscfdna <- ls[grep("cfDNA",ls)]
lscfdna <- lscfdna[grep(".beta", lscfdna)]
c <- c()
m <- matrix(0, nrow=28217448, ncol=2)
for (file in lscfdna) {
  print(file)
  fname <- file.path(loc, file)
  N <- file.info(fname)$size
  content <- matrix(readBin(fname, "integer", N, size = 1, signed = FALSE), N / 2, 2, byrow=TRUE)
  print(length(which(content[,2] > 10)) / nrow(content))
  print(mean(content[,2]))
  c <- c(c, mean(content[,2]))
  m <- m + content
}
included <- which(m[,2] >= 750)
t <- t[included,]
m <- m[included,]
included <- which(t$V1 %in% paste0("chr", c(1:22)))
t <- t[included,]
m <- m[included,]
m_df <- data.frame(m)
colnames(m_df) <- c("meth", "all")
m_df$index <- t$V3
m_df_small <- m_df
m_df_small$beta  <- m_df_small$meth / m_df_small$all
m_df_small <- m_df_small[,c(3,4)]
q <- nrow(m_df_small)
q / 3
saveRDS(m_df_small[c(1:round(q/3, digits = 0)),], file = here("data/CpG_Loyfer_1-3.rds"))
saveRDS(m_df_small[c(round((q/3)+ 1, digits = 0) : round((2*q/3), digits = 0)),], file = here("data/CpG_Loyfer_2-3.rds"))
saveRDS(m_df_small[c(round((2*q/3)+1, digits = 0) : q),], file = here("data/CpG_Loyfer_3-3.rds"))
```


## Process the data

  *code/Loyfer_combined.sh* -> outputs "Loyfer_combined"
    Extracts per case the amount of fragments starting at and around the CpGs in the Loyfer data
  

## Combine the data from the different cases, overlapping the Loyfer data

```{r}
loc <- here(outdir, "Loyfer_combined")
ls <- list.files(loc)
t <- tibble()
annots <- c('hg19_cpgs')
annots <- build_annotations(genome = 'hg19', annotations = annots)
for (file in ls) {
  print(file)
  temp <- readRDS(file.path(loc, file))
  temp$beta <- round(temp$beta, digits =2)
  temp <- temp[which(temp$seq %in% c("ACG", "CCG", "GCG", "TCG", "ACCG", "CCCG", "GCCG", "TCCG")),]
  temp_gr <- GRanges(temp$pos)
  o <- as_tibble(as.data.frame(findOverlaps(temp_gr, annots)))
  temp$group <- "NA"
  temp[o$queryHits,]$group <- annots[o$subjectHits]$type
  temp <- temp %>%
    group_by(seq, beta, group) %>%
    summarise(start= sum(start), over = sum(over), ratio = sum(start)/sum(over))
  t <- rbind(t, temp)
}
t <-t %>%
  group_by(seq, beta, group) %>% 
  summarise(start= sum(start), over = sum(over), ratio = sum(start)/sum(over))
saveRDS(t, here("data/Loyfer_50_ratios.rds"))
```
